---
title: "hw 5.5.2"
author: "siyu"
date: "2023-02-06"
output: html_document
---

```{r}
library(nycflights13)
library(tidyverse)

#filter()
#arrange()
#select()
#mutate()
#summarize()
#group_by()

```

1. 
```{r}
mutate(flights, 
       dep_time_mins=dep_time%/%100*60+dep_time%%100,
       sched_dep_time_mins=sched_dep_time%/%100*60+sched_dep_time%%100)
```

2. 
For a lot of flights air_time does not equal arr_time-dep_time, which is different from what I expected. In my understanding air time is the time a plane stays in the air, while arrival time and departure times are the exact time when the plane goes through a "gate" in the airport(...?). I don't know how to fix this as they are different concepts. 
```{r}
mutate(flights,
       air_time2=arr_time-dep_time)
```

3. 
I expect dep_delay to be equal to sched_dep_time-dep_time. This is true for some flights but not the others. I believe this is because some flights were scheduled before midnight but departed after midnight, thus creating an "error" in the actual departing time recorded and resulting in the difference. 
```{r}
mutate(flights,
       dep_delay_diff=dep_time-sched_dep_time)
```